Untitled

### 2017-02-02 Manuscript/Manuscript using actual data.Rmd
fixed order in plots

bw_dat <- tidyr::spread(bw_dat, year, LE_wbgap) 
names(bw_dat)[3:6] <- c("first.gap","second.gap", "third.gap", "fourth.gap")  
bw_dat <- bw_dat %>% mutate(era1.diff = first.gap - second.gap,
                            era2.diff = second.gap - third.gap,
                            era3.diff = third.gap - fourth.gap,
                            state.gdiff.order.1 = reorder(state, first.gap),
                            state.gdiff.num.1 = as.numeric(state.gdiff.order.1),
                            state.gdiff.order.2 = reorder(state, second.gap),
                            state.gdiff.num.2 = as.numeric(state.gdiff.order.2),
                            state.gdiff.order.3 = reorder(state, third.gap),
                            state.gdiff.num.3 = as.numeric(state.gdiff.order.3)
)

cod.df <- data.frame(state = factor(), sex = factor(), era = character(), COD = factor(), Contribution.to.change = numeric(), Contrib.to.change.prop = numeric(), narrowed_gap = logical())
age.df <- data.frame(state = factor(), sex = factor(), era = character(), age_minbin = numeric(), Contribution.to.change = numeric(), Contrib.to.change.prop = numeric(), narrowed_gap = logical())

@@

cod.df2 <- merge(cod.df, bw_dat, by = c("state", "sex"))
cod.df2 <- cod.df2 %>% mutate(new.start.1 = -start + first.gap, new.finish.1 = -finish + first.gap,
                              new.start.2 = -start + second.gap, new.finish.2 = -finish + second.gap,
                              new.start.3 = -start + third.gap, new.finish.3 = -finish + third.gap)

y.labels <- levels(factor(cod.df2$state.gdiff.order.1))
y.num.breaks <- length(levels(factor(cod.df2$state.gdiff.order.1)))

ggplotly(
  ggplot(subset(cod.df2, sex == "Male" & era == "1969-1983"), aes(y = state.gdiff.num.1, x = new.start.1)) +
    geom_rect(aes(xmin = new.start.1, ymin = state.gdiff.num.1 - 0.45, 
                  ymax = state.gdiff.num.1 + 0.45, 
                  xmax = new.finish.1, fill = COD), 
              color = "white") +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = second.gap, xend= second.gap, y = state.gdiff.num.1 - 0.5, yend = state.gdiff.num.1 + 0.5)) +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = first.gap, xend= first.gap, y = state.gdiff.num.1 - 0.5, yend = state.gdiff.num.1 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks, labels = y.labels)) %>% 
  layout(xaxis = list(title = "Life expectancy gap (years): 1969-1983"), yaxis = list(title = NA, autorange = "reversed"))

@@

```{r}
y.labels.2 <- levels(factor(cod.df2$state.gdiff.order.2))
y.num.breaks.2 <- length(levels(factor(cod.df2$state.gdiff.order.2)))

ggplotly(
  ggplot(subset(cod.df2, sex == "Male" & era == "1983-1993"), aes(y = state.gdiff.num.2, x = new.start.2)) +
    geom_rect(aes(xmin = new.start.2, ymin = state.gdiff.num.2 - 0.45, 
                  ymax = state.gdiff.num.2 + 0.45, 
                  xmax = new.finish.2, fill = COD), 
              color = "white") +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = third.gap, xend= third.gap, y = state.gdiff.num.2 - 0.5, yend = state.gdiff.num.2 + 0.5)) +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = second.gap, xend= second.gap, y = state.gdiff.num.2 - 0.5, yend = state.gdiff.num.2 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks.2, labels = y.labels.2)) %>% 
  layout(xaxis = list(title = "Life expectancy gap (years): 1969-1983"), yaxis = list(title = NA, autorange = "reversed"))
```

@@

```{r}
y.labels.3 <- levels(factor(cod.df2$state.gdiff.order.3))
y.num.breaks.3 <- length(levels(factor(cod.df2$state.gdiff.order.3)))

ggplotly(
  ggplot(subset(cod.df2, sex == "Male" & era == "1993-2013"), aes(y = state.gdiff.num.3, x = new.start.3)) +
    geom_rect(aes(xmin = new.start.3, ymin = state.gdiff.num.3 - 0.45, 
                  ymax = state.gdiff.num.3 + 0.45, 
                  xmax = new.finish.3, fill = COD), 
              color = "white") +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = fourth.gap, xend= fourth.gap, y = state.gdiff.num.3 - 0.5, yend = state.gdiff.num.3 + 0.5)) +
    geom_segment(data = subset(bw_dat, sex == "Male"), 
                 aes(x = third.gap, xend= third.gap, y = state.gdiff.num.3 - 0.5, yend = state.gdiff.num.3 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks.3, labels = y.labels.3)) %>% 
  layout(xaxis = list(title = "Life expectancy gap (years): 1993-2013"), yaxis = list(title = NA, autorange = "reversed"))
```

>>>>

bw_dat <- tidyr::spread(bw_dat, year, LE_wbgap) 
names(bw_dat)[3:6] <- c("first.gap","second.gap", "third.gap", "fourth.gap")  
bw_dat.males <- bw_dat %>% filter(sex == "Male") %>%
  mutate(era1.diff = first.gap - second.gap,
         era2.diff = second.gap - third.gap,
         era3.diff = third.gap - fourth.gap,
         state.gdiff.order.1 = reorder(state, first.gap),
         state.gdiff.num.1 = as.numeric(state.gdiff.order.1),
         state.gdiff.order.2 = reorder(state, second.gap),
         state.gdiff.num.2 = as.numeric(state.gdiff.order.2),
         state.gdiff.order.3 = reorder(state, third.gap),
         state.gdiff.num.3 = as.numeric(state.gdiff.order.3)
  )

bw_dat.females <- bw_dat %>% filter(sex == "Female") %>%
  mutate(era1.diff = first.gap - second.gap,
         era2.diff = second.gap - third.gap,
         era3.diff = third.gap - fourth.gap,
         state.gdiff.order.1 = reorder(state, first.gap),
         state.gdiff.num.1 = as.numeric(state.gdiff.order.1),
         state.gdiff.order.2 = reorder(state, second.gap),
         state.gdiff.num.2 = as.numeric(state.gdiff.order.2),
         state.gdiff.order.3 = reorder(state, third.gap),
         state.gdiff.num.3 = as.numeric(state.gdiff.order.3)
  )

cod.df <- data.frame(state = factor(), sex = factor(), era = character(), 
                     COD = factor(), Contribution.to.change = numeric(), 
                     Contrib.to.change.prop = numeric(), narrowed_gap = logical())

age.df <- data.frame(state = factor(), sex = factor(), era = character(), 
                     age_minbin = numeric(), Contribution.to.change = numeric(), 
                     Contrib.to.change.prop = numeric(), narrowed_gap = logical())

@@

cod.df.males <- merge(subset(cod.df, sex == "Male"), bw_dat.males, by = c("state"))
cod.df.males <- cod.df.males %>% mutate(new.start.1 = -start + first.gap, new.finish.1 = -finish + first.gap,
                                        new.start.2 = -start + second.gap, new.finish.2 = -finish + second.gap,
                                        new.start.3 = -start + third.gap, new.finish.3 = -finish + third.gap)

y.labels <- levels(factor(cod.df.males$state.gdiff.order.1))
y.num.breaks <- length(levels(factor(cod.df.males$state.gdiff.order.1)))

ggplotly(
  ggplot(subset(cod.df.males, era == "1969-1983"), aes(y = state.gdiff.num.1, x = new.start.1)) +
    geom_rect(aes(xmin = new.start.1, ymin = state.gdiff.num.1 - 0.45, 
                  ymax = state.gdiff.num.1 + 0.45, 
                  xmax = new.finish.1, fill = COD), 
              color = "white") +
    geom_segment(data = bw_dat.males,
                 aes(x = second.gap, xend= second.gap, y = state.gdiff.num.1 - 0.5, yend = state.gdiff.num.1 + 0.5)) +
    geom_segment(data = bw_dat.males,
                 aes(x = first.gap, xend= first.gap, y = state.gdiff.num.1 - 0.5, yend = state.gdiff.num.1 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks, labels = y.labels)) %>%
  layout(xaxis = list(title = "Life expectancy gap (years): 1969-1983"), yaxis = list(title = NA, autorange = "reversed"))

@@

```{r}
y.labels.2 <- levels(factor(cod.df.males$state.gdiff.order.2))
y.num.breaks.2 <- length(levels(factor(cod.df.males$state.gdiff.order.2)))

ggplotly(
  ggplot(subset(cod.df.males, era == "1983-1993"), aes(y = state.gdiff.num.2, x = new.start.2)) +
    geom_rect(aes(xmin = new.start.2, ymin = state.gdiff.num.2 - 0.45, 
                  ymax = state.gdiff.num.2 + 0.45, 
                  xmax = new.finish.2, fill = COD), 
              color = "white") +
    geom_segment(data = bw_dat.males, 
                 aes(x = third.gap, xend= third.gap, y = state.gdiff.num.2 - 0.5, yend = state.gdiff.num.2 + 0.5)) +
    geom_segment(data = bw_dat.males, 
                 aes(x = second.gap, xend= second.gap, y = state.gdiff.num.2 - 0.5, yend = state.gdiff.num.2 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks.2, labels = y.labels.2)) %>% 
  layout(xaxis = list(title = "Life expectancy gap (years): 1969-1983"), yaxis = list(title = NA, autorange = "reversed"))
```

@@

```{r}
y.labels.3 <- levels(factor(cod.df.males$state.gdiff.order.3))
y.num.breaks.3 <- length(levels(factor(cod.df.males$state.gdiff.order.3)))

ggplotly(
  ggplot(subset(cod.df.males, era == "1993-2013"), aes(y = state.gdiff.num.3, x = new.start.3)) +
    geom_rect(aes(xmin = new.start.3, ymin = state.gdiff.num.3 - 0.45, 
                  ymax = state.gdiff.num.3 + 0.45, 
                  xmax = new.finish.3, fill = COD), 
              color = "white") +
    geom_segment(data = bw_dat.males, 
                 aes(x = fourth.gap, xend= fourth.gap, y = state.gdiff.num.3 - 0.5, yend = state.gdiff.num.3 + 0.5)) +
    geom_segment(data = bw_dat.males, 
                 aes(x = third.gap, xend= third.gap, y = state.gdiff.num.3 - 0.5, yend = state.gdiff.num.3 + 0.5), lty = 3) +
    theme_minimal() + scale_y_continuous(breaks = 1:y.num.breaks.3, labels = y.labels.3)) %>% 
  layout(xaxis = list(title = "Life expectancy gap (years): 1993-2013"), yaxis = list(title = NA, autorange = "reversed"))
```
